Constraints on Assembly Bias from Galaxy Clustering.

### 2016-06-07 ms.tex
additional changes in intro
Still need to add some sentences promoting a
smooth transition between what I wrote and what Andrew wrote…..

Additional support for the presence of assembly bias has come from a
variety of studies that have shown, or suggested, that the large-scale
environment (i.e., clustering strength) of dark matter haloes {\it of
  fixed mass} is correlated with the star formation rate of their
central
galaxies\citep[][]{yang_etal06a,blanton_berlind07,wang_etal08,tinker_etal12,wang_etal13,HW13a,hearin_etal13b,hearin_etal14,watson_etal14}.
However, a recent study by \citet{lin_mandelbaum_etal15} argues that
most of the these differences in clustering strength can be explained
as due to differences in halo mass or contamination by satellite
galaxies. \citet{lin_mandelbaum_etal15} therefore argue that there is
no significant evidence for assembly bias in galaxy-scale halos
\citep[see also][]{paranjape15}.

\citet{yang_etal06a}, who showed that the clustering strength of
galaxy groups (i.e., dark matter haloes) of fixed mass is correlated
with the star formation rate of their central galaxy. Similar
conclusions have been reached by a number of independent
studies\citep[][]{blanton_berlind07,wang_etal08,tinker_etal12,wang_etal13,hearin_etal14}. However,
\citet{lin_mandelbaum_etal15} have argued that these differences in
clustering strength can all be explained as due to differences in halo
mass or contamination by satellite galaxies and concluded that there
is no significant evidence for assembly bias in galaxy-scale halos
\citep[see also][]{paranjape15}.

In addition, Hearin etal have argued that the large-scale conformity
in galaxy star formation rates observed by Kauffmann etal is another
`smoking-gun' signature of assembly bias (but see Parajape etal 2015).

halos with quenched centrals are
more strongly clustered than halos of the same mass that host star
forming centrals \citep[see
  also][]{blanton_berlind07,wang_etal08,wang_etal13}

Using galaxy-group cross correlations, Ref. [61] has shown that halos
with quenched centrals are more strongly clustered than halos of the
same mass that host star forming centrals. This first observational
evidence for galaxy assembly bias has been confirmed using larger data
sets [62, 63]. F

Further evidence for assembly bias from group catalogs
has come from Ref. [64], who found that the color/SFR of satellite
galaxies depend on the color/SFR of the group’s central galaxy, again
at fixed halo mass, a phenomenon dubbed galactic conformity.  More
recently, Ref. [65] demonstrated that correlations between the SFRs of
central galaxies and their neighboring galaxies persist out to many
Mpc, far beyond the virial radii of their host halos.  Quenched
central galaxies preferentially reside in large-scale environments
replete with quenched galaxies. Both these conformity signals indicate
manifest violations of the Mass-Only ansatz [66].  A different
approach was taken by Ref. [67], who shuffled the colors and
luminosities of galaxies in groups of similar mass, preserving for
each galaxy its group-centric distance. This procedure preserves the
halo occupation N|Mh, but erases the relationship between the
galaxies and the larger-scale environments of the groups in which they
reside. The Mass-Only ansatz predicts that the real and shuffled group
catalogs should reveal identical clustering. Contrarily, the
clustering in the two catalogs differ at the ∼ 5% (∼ 10%) level on
scales larger
                                     % (smaller) than ∼ 1 h

In addition to these studies that have focussed on constraining the
relation between a {\it primary} galaxy property (e.g., luminosity or
stellar mass) and a {\it primary} halo property (e.g., $M$ or
$\vmax$), there have also been a number of studies that relate
{\it secondary} galaxy properties (e.g., color or specific star
formation rate) to a {\it secondary} halo property (e.g., halo
formation time or concentration). The archetype of these model is the
`age-matching' model developed by \citet{HW13a}, in which galaxy color
is rank-order matched, at fixed stellar mass, to some quantity related
to the assembly history of the galaxy's (sub)halo.
Paranjape \etal 2015...

Another approach that 
This was taken one step further by Hearin ccc, who developed an
extension of SHAM, called age-matching. In age-matching a

>>>>

Additional support for the presence of assembly bias has come from a
variety of studies that have shown, or suggested, that the large-scale
environment (i.e., clustering strength) of dark matter haloes {\it of
  fixed mass} is correlated with the star formation rate of their
central
galaxies\citep[][]{yang_etal06a,blanton_berlind07,wang_etal08,tinker_etal12,wang_etal13,HW13a,hearin_etal13b,hearin_etal14,watson_etal14}.
However, \citet{lin_mandelbaum_etal15} claim that most of the these
differences in clustering strength can be explained as due to
differences in halo mass or contamination by satellite galaxies, and
therefore argue that there is no significant evidence for assembly
bias in galaxy-scale halos \citep[see also][]{paranjape15}.  On the
other hand, \citet{miyatake_etal15} and \citet{more_etal16} recently
presented strong evidence for the presence of assembly bias in massive
clusters; in particular, they find that clusters with a more
concentrated distribution of satellite galaxies are less strongly
clustered than their equal-mass counterparts whose satellite galaxies
are less centrally concentrated. To summarize, while there is strong
evidence for the presence of assembly bias on the scale of clusters,
there is not concensus yet as to whether assembly bias plays also a
role in less massive haloes.
